Quantifying social distancing behaviour across Australia in response to COVID-19

### 2020-05-04 manuscript/ms.Rmd

Australia --- and many other countries with intensive physical distancing measures in place --- is now shifting its focus from reacting to a first epidemic wave of COVID-19 to proactive planning for gradual and targeted relaxation of physical distancing measures. Quantifying how the behaviour of the population has changed in response to these measures and the potential impact on disease transmission is critical for the next stage of response planning.

>>>>

Australia --- and many other countries with intensive physical distancing measures in place --- is now shifting its focus from reacting to a first epidemic wave of COVID-19 to proactive planning for gradual and targeted relaxation of physical distancing measures. Quantifying how the behaviour of the population has changed in response to these measures and the potential impact on disease transmission is critical for the next stage of epidemic planning and response.
